Prepare Data

### 2021-05-07 report/draft.Rmd
adapt figures

# Data, Measurement & Method

```{r dv, fig.align = 'center', out.width = "75%", fig.cap = "Descriptive Overview Dependent Variable"}
include_graphics(here("report/figures", "Dependent Variable-1.png"))
```

@@

```{r balance, fig.align = 'center', out.width = "75%", fig.cap = "Balance Checks"}
include_graphics(here("report/figures", "balance-checks-1.png"))
```

@@

\newpage 
\blandscape 
```{r results-hs, fig.align = 'center', fig.cap = "Results"}
include_graphics(here("report/figures", "save-patchwork-results-1.png"))
```
\elandscape

>>>>

**Gender hypothesis** (_H1a_):  Women politicians are evaluated lower when striking a political compromise compared to men politicians.

**Gender hypothesis** (_H1b_):  Women politicians are evaluated lower when not striking a political compromise compared to men politicians.

**Migration hypothesis** (_H2_): Politicians with a migration background are evaluated lower when striking a political compromise compared to politicians without a migration background.

**Intersection hypothesis** (_H3a_): Women politician with a migration background are evaluated lower when striking a political compromise compared to men politicians without a migration background.

**Intersection hypothesis** (_H3b_): Women politician with a migration background are evaluated lower when not striking a political compromise compared to men politicians without a migration background.

# Data, Measurement & Method
The survey experiment is conducted in the Netherlands between the 21st of April 2021 and the 4th of May 2021.
**WHY NL**

## Data
Participants were told that they are taking part in a survey to get an overview of how Dutch people form their views on politics.
The sample, recruited through [KiesKompas](https://www.kieskompas.nl/en/),  consists of 2,004 participants of 18 years and older.[^1]
Because Kieskompas works with non-random opt-in respondents, I have measured many demographic and political background variables (described in [Section 3.2](#measurement) under _Covariates_).
Balance checks are conducted to demonstrate whether certain categories are over represented in a certain experimental group (see [Section 3.3](#method), Figure \ref{fig:balance}).
The study has been approved by the [Research Ethics Review Committee](https://fsw.vu.nl/nl/onderzoek/research-ethics-review/index.aspx) of the _Vrije Universiteit Amsterdam_ (see the approval [here](https://github.com/MarikenvdVelden/compromise-punish/blob/main/docs/EthicalApproval.pdf)).
To ensure good quality of our data, two attention checks (discussed in more detail in [Section 3.3 of the Pre-Analysis Plan](https://github.com/MarikenvdVelden/bend-break-compromise/blob/main/docs/pap/compromise-punishment-pap.pdf)) are included.
All respondents included in the analyses passed both attention checks.

[^1]: The sample is calculated based on a power analysis presented in the [Pre-Analysis Plan](https://github.com/MarikenvdVelden/bend-break-compromise/blob/main/docs/pap/compromise-punishment-pap.pdf).

## Measurement

**_Dependent Variables_**
I rely on four measures reflecting different aspects of how people judge politicians.
The evaluation of politicians' character traits are statements deriving from @aaldering2016political.
The other three neasures to evaluate the politician of the treatment are translated from @bauer2017punished -- i.e. favorability, representation, and career perspectives.
General favorability is shown to be related to vote choice [@elis2010dynamics], perceptions of represenation are related to legislative compromise and cooperation [@doherty2013whom], and career perspective is included because critiques of women are typically manifested in their leadership skills [@eagly2007female].

```{r dv, fig.align = 'center', out.width = "90%", fig.cap = "\\label{fig:descr_dv}Descriptive Overview Dependent Variable"}
include_graphics(here("report/figures", "Dependent Variable-1.png"))
```

**_Experimental Conditions_**
The stimuli in the experiment are news messages in the same style as the Dutch news website [nu.nl](https://www.nu.nl/).
In these news messages, we manipulate: a) the _gender_ of the politician (male vs. female); b) the _migration background_ of the politician (based on a Arabic sounding name (Rachid(a) Amezian) or a native Dutch sounding name (Karel/Karin van der Kleijn)); and c) whether the politician _striked a compromise or not_.
This creates a full `2*2*2` factorial experiment with four rounds (see Table \ref{tab:treat}).
Every round, the news message covers a new issue.
The issues are: "defense" (increase cooperation of the defense units), "immigration" (immigration stop in western countries), "education" (expansion creative elementary school activities), "COVID-19" (emergency legislation to combat the COVID-19 pandemic).
For every round, the politicians' name, and thereby gender and immigration background, are manipulated in the text and in the picture, as well as the decision to strike a compromise.

```{r stimulus, topcaption=TRUE}
d <- tibble(` ` = c(1:8),
            `Name Politician` = c(rep("Rachid Amezian", 2), rep("Karel van der Kleijn", 2),
                                  rep("Rachida Amezian", 2), rep("Karin van der Kleijn", 2)),
            Gender = c(rep("Men",4), rep("Women", 4)),
            `Migration Background` = c(rep("Yes", 2), rep("No", 2),
                                  rep("Yes", 2), rep("No", 2)),
            Compromise = c("Yes", "No", "Yes", "No", "Yes", "No", "Yes", "No"))

kbl(d, booktabs =T, caption = "\\label{tab:treat}Experimental Conditions",
    align = c("l", "l", "c", "c", "c")) %>%
  kable_styling(latex_options = c("striped", "hold_position"),
                full_width = F, fixed_thead = T, position = "center") %>%
  column_spec(1, width = ".5cm") %>%
  column_spec(2, width = "3.2cm") %>%
  column_spec(3, width = "2.5cm")%>%
  column_spec(4, width = "3.5cm")%>%
  column_spec(5, width = "2.5cm")

```

The text of the treatment is a Dutch translation of the stimulus material developed by @bauer2017punished.
The authors have pre-tested the text of the stimuli material several times [see the [Web Appendix](https://static-content.springer.com/esm/art%3A10.1007%2Fs11109-016-9356-6/MediaObjects/11109_2016_9356_MOESM1_ESM.docx) of @bauer2017punished].
The photo's of their stimuli material can unfortunately not be used, because a) @bauer2017punished only investigate the difference between men and women politicians, using solely photo''s of caucasians; and b) the American flag was present in their material.
Instead, I have used photo's from local politicians of the city of The Hague that are not know to the general public. 
The men politicians are in real life representatives of the [liberal-progressive party D66](https://www.denhaag.nl/nl/bestuur-en-organisatie/gemeenteraad/raadsleden-en-fractievertegenwoordigers/boutkabout-a.-abid-fractievertegenwoordiger-d66.htm) (man with immigrant background) and of the [christian democratic party CDA](https://www.denhaag.nl/nl/bestuur-en-organisatie/gemeenteraad/raadsleden-en-fractievertegenwoordigers/groot-de-d.p.-daniel-fractievertegenwoordiger-cda.htm) (man without immigrant background).
The women politicians are in real life representatives of a [right-wing populist party _Hart voor Den Haag/ Groep de Mos_](https://www.denhaag.nl/nl/bestuur-en-organisatie/gemeenteraad/raadsleden-en-fractievertegenwoordigers/davituliani-n.-nino-raadslid-hart-voor-den-haaggroep-de-mos.htm) (woman with migration background) and of the [social democratic party PvdA](https://www.denhaag.nl/nl/bestuur-en-organisatie/gemeenteraad/raadsleden-en-fractievertegenwoordigers/holman-j.-janneke-raadslid-pvda.htm) (woman without immigrant background).
Thereby we have a spread over the ideological different parties present in Dutch politics.
The names for the politicians without immigration background are _Karel_ (man) and _Karin_ (woman) _van der Kleijn_, which are typical native Dutch names.
For the politicians with an immigration background, we picked _Rachid_ (man) and _Rachida_ (woman) _Amezian_.
All stimulus material is developed by the [Network Institute of the _Vrije Universiteit Amsterdam_](https://networkinstitute.org/) and can be accessed [here](https://github.com/MarikenvdVelden/compromise-punish/tree/main/docs/pap/treatments).

**_Covariates_**

@@

## Method

```{r balance, fig.align = 'center', out.width = "95%", fig.cap = "\\label{fig:balance}Balance Checks"}
include_graphics(here("report/figures", "balance-checks-1.png"))
```

@@

## Pre-Registered Hypotheses
\newpage 
\blandscape 
```{r results-hs, out.width = "95%", fig.align = 'center', fig.cap = "\\label{fig:results}Results"}
include_graphics(here("report/figures", "save-patchwork-results-1.png"))
```
\elandscape

## Exploration

### 2021-05-07 src/analysis/Analysis.Rmd
adapt figures

```{r "visualize-unbalanced-vars", fig.height=10, fig.width=10}
source(here("src/analysis/distribution_unbalanced_vars.R"))

p1 + p2 + p3 + p4 + plot_layout(ncol=2)
```

## Gender Hypothesis 
```{r "h1", fig.align="center", fig.height=8, fig.width=8}
source(here("src/analysis/h1.R"))
h1
```

## Migration Hypothesis
```{r "h2", fig.align="center", fig.height=8, fig.width=8}
source(here("src/analysis/h2.R"))
h2
```

## Intersection Hypothesis
```{r "h3", fig.align="center", fig.height=8, fig.width=8}
source(here("src/analysis/h3.R"))
h3
```

## Intersection Hypothesis -- Pooled
```{r "h3-pooled", fig.align="center", fig.height=6, fig.width=6}
source(here("src/analysis/h3-pooled.R"))
h3p
```

```{r "save-patchwork-results", echo = F, fig.show="hide", fig.height= 15, fig.width=15}
h1 + h2 + h3 + h3p + plot_layout(ncol=2)
```

>>>>

```{r "visualize-unbalanced-vars", fig.height=15, fig.width=20}
source(here("src/analysis/distribution_unbalanced_vars.R"))
p1 + p2 + p3 + p4 + plot_layout(ncol=2)
```

## Gender Hypothesis 
```{r "h1", fig.align="center", fig.height=8, fig.width=8}
source(here("src/analysis/h1.R"))
p1
```

## Migration Hypothesis
```{r "h2", fig.align="center", fig.height=8, fig.width=8}
source(here("src/analysis/h2.R"))
p2
```

## Intersection Hypothesis
```{r "h3", fig.align="center", fig.height=8, fig.width=8}
source(here("src/analysis/h3.R"))
p3
```

## Intersection Hypothesis -- Pooled
```{r "h3-pooled", fig.align="center", fig.height=6, fig.width=6}
source(here("src/analysis/h3-pooled.R"))
p3p
```

```{r "save-patchwork-results", echo = F, fig.show="hide", fig.height= 15, fig.width=20}
p1 + p2 + p3 + p3p + plot_layout(ncol=2)
```

### 2021-05-07 src/data-processing/prep_data.Rmd
adapt figures

### Dependent Variable
```{r "Dependent Variable", echo=F}
d %>%
  mutate(PT_D1 = round((PT_D1_1 + PT_D1_2 + PT_D1_3 + PT_D1_4 + PT_D1_5 + PT_D1_6)/6, 0),
         PT_E1 = round((PT_E1_1 + PT_E1_2 + PT_E1_3 + PT_E1_4 + PT_E1_5 + PT_E1_6)/6, 0),
         PT_C1 = round((PT_C1_1 + PT_C1_2 + PT_C1_3 + PT_C1_4 + PT_C1_5 + PT_C1_6)/6, 0),
         PT_I1 = round((PT_I1_1 + PT_I1_2 + PT_I1_3 + PT_I1_4 + PT_I1_5 + PT_I1_6)/6, 0),
         PreT5 = round((PreT5_1 + PreT5_2 + PreT5_3 + PreT5_4)/4,0),
         PreT7 = round((PreT7_1 + PreT7_2 + PreT7_3 + PreT7_4 + PreT7_5 + PreT7_6 + PreT7_7)/7,0)) %>%
  pivot_longer(cols = c(name_D, name_I, name_E, name_C),
               values_to = "name",
               names_to = "issue") %>%
  drop_na(name) %>%
  mutate(issue = recode(issue, 
                        name_C = "COVID_19",
                        name_D = "Defense",
                        name_E = "Education",
                        name_I = "Immigration")) %>%
  pivot_longer(cols = c(PT_D1, PT_E1, PT_C1, PT_I1),
               values_to = "PT1",
               names_to = "issue1") %>%
  drop_na(PT1) %>%
  mutate(issue1 = recode(issue1, 
                        PT_C1 = "COVID_19",
                        PT_D1 = "Defense",
                        PT_E1 = "Education",
                        PT_I1 = "Immigration")) %>%
  pivot_longer(cols = c(PT_D2, PT_E2, PT_C2, PT_I2),
               values_to = "PT2",
               names_to = "issue2") %>%
  mutate(issue2 = recode(issue2, 
                        PT_C2 = "COVID_19",
                        PT_D2 = "Defense",
                        PT_E2 = "Education",
                        PT_I2 = "Immigration")) %>%
  pivot_longer(cols = c(PT_D3, PT_E3, PT_C3, PT_I3),
               values_to = "PT3",
               names_to = "issue3") %>%
  mutate(issue3 = recode(issue3, 
                         PT_C3 = "COVID_19",
                         PT_D3 = "Defense",
                         PT_E3 = "Education",
                         PT_I3 = "Immigration")) %>%
  pivot_longer(cols = c(PT_D4, PT_E4, PT_C4, PT_I4),
               values_to = "PT4",
               names_to = "issue4") %>%
  mutate(issue4 = recode(issue4, 
                         PT_C4 = "COVID_19",
                         PT_D4 = "Defense",
                         PT_E4 = "Education",
                         PT_I4 = "Immigration"),
        check = if_else(issue == issue1 & issue == issue2 & issue == issue3 & issue == issue4, 1,0)) %>%
  filter(check == 1) %>%
  select(PT1, PT2, PT3, PT4, issue = issue1) %>%
  pivot_longer(cols = PT1:PT4,
               names_to = "dvs") %>%
  mutate(dvs = recode(dvs,
                       PT1 = "DV: Trait Evaluation",
                       PT2 = "DV: Favorability",
                       PT3 = "DV: Representation",
                       PT4 = "DV: Career Prospects")) %>%
  group_by(issue, dvs) %>%
  summarise(means = mean(value, na.rm=T),
            stdev = sd(value, na.rm=T)) %>%
  mutate(lower = means - (1.56 * stdev),
         upper = means + (1.56 * stdev)) %>%
  ggplot(aes(x = dvs, y = means, colour = issue,
             ymin = lower, ymax = upper, label = issue)) +
  geom_point(position = position_dodge(.2)) + 
  geom_errorbar(position = position_dodge(.2), width = 0) +
  geom_label_repel(nudge_x = 0.35,nudge_y = 0.5, size = 4) + 
  labs(y = "0 (negative) - 10 (positive)", 
       x = "", title = "Evaluation of Politicians") +
  geom_hline(yintercept = 5, linetype = "dotted", color = "darkgrey") +
  theme_minimal() +
  scale_color_manual(values = fig_cols) +
  coord_flip() +
  theme(plot.title = element_text(hjust = 0.5),
        legend.position="none",
        legend.title = element_blank()) 
```

>>>>

### Dependent Variable
```{r "Dependent Variable", echo=F, fig.width=10, fig.height=8}
d %>%
  mutate(PT_D1 = round((PT_D1_1 + PT_D1_2 + PT_D1_3 + PT_D1_4 + PT_D1_5 + PT_D1_6)/6, 0),
         PT_E1 = round((PT_E1_1 + PT_E1_2 + PT_E1_3 + PT_E1_4 + PT_E1_5 + PT_E1_6)/6, 0),
         PT_C1 = round((PT_C1_1 + PT_C1_2 + PT_C1_3 + PT_C1_4 + PT_C1_5 + PT_C1_6)/6, 0),
         PT_I1 = round((PT_I1_1 + PT_I1_2 + PT_I1_3 + PT_I1_4 + PT_I1_5 + PT_I1_6)/6, 0),
         PreT5 = round((PreT5_1 + PreT5_2 + PreT5_3 + PreT5_4)/4,0),
         PreT7 = round((PreT7_1 + PreT7_2 + PreT7_3 + PreT7_4 + PreT7_5 + PreT7_6 + PreT7_7)/7,0)) %>%
  pivot_longer(cols = c(name_D, name_I, name_E, name_C),
               values_to = "name",
               names_to = "issue") %>%
  drop_na(name) %>%
  mutate(issue = recode(issue, 
                        name_C = "COVID",
                        name_D = "Defense",
                        name_E = "Education",
                        name_I = "Immigration")) %>%
  pivot_longer(cols = c(PT_D1, PT_E1, PT_C1, PT_I1),
               values_to = "PT1",
               names_to = "issue1") %>%
  drop_na(PT1) %>%
  mutate(issue1 = recode(issue1, 
                        PT_C1 = "COVID",
                        PT_D1 = "Defense",
                        PT_E1 = "Education",
                        PT_I1 = "Immigration")) %>%
  pivot_longer(cols = c(PT_D2, PT_E2, PT_C2, PT_I2),
               values_to = "PT2",
               names_to = "issue2") %>%
  mutate(issue2 = recode(issue2, 
                        PT_C2 = "COVID",
                        PT_D2 = "Defense",
                        PT_E2 = "Education",
                        PT_I2 = "Immigration")) %>%
  pivot_longer(cols = c(PT_D3, PT_E3, PT_C3, PT_I3),
               values_to = "PT3",
               names_to = "issue3") %>%
  mutate(issue3 = recode(issue3, 
                         PT_C3 = "COVID",
                         PT_D3 = "Defense",
                         PT_E3 = "Education",
                         PT_I3 = "Immigration")) %>%
  pivot_longer(cols = c(PT_D4, PT_E4, PT_C4, PT_I4),
               values_to = "PT4",
               names_to = "issue4") %>%
  mutate(issue4 = recode(issue4, 
                         PT_C4 = "COVID",
                         PT_D4 = "Defense",
                         PT_E4 = "Education",
                         PT_I4 = "Immigration"),
        check = if_else(issue == issue1 & issue == issue2 & issue == issue3 & issue == issue4, 1,0)) %>%
  filter(check == 1) %>%
  select(PT1, PT2, PT3, PT4, issue = issue1) %>%
  mutate(PT1 = PT1 * 2) %>%
  #mutate_at(c("PT1", "PT2", "PT3", "PT4"), ~(scale(.) %>% as.vector)) %>%
  pivot_longer(cols = PT1:PT4,
               names_to = "dvs") %>%
  mutate(dvs = recode(dvs,
                       PT1 = "DV: Trait Evaluation",
                       PT2 = "DV: Favorability",
                       PT3 = "DV: Representation",
                       PT4 = "DV: Career Prospects")) %>%
  group_by(issue, dvs) %>%
  summarise(means = mean(value, na.rm=T),
            stdev = sd(value, na.rm=T)) %>%
  mutate(lower = means - (1.56 * stdev),
         upper = means + (1.56 * stdev)) %>%
  ggplot(aes(x = dvs, y = means, colour = issue,
             ymin = lower, ymax = upper, label = issue)) +
  geom_point(position = position_dodge(.5)) + 
  geom_errorbar(position = position_dodge(.5), width = 0) +
  geom_text(aes(y = upper +.5), 
            position = position_dodge(.5),na.rm = TRUE) + 
  labs(y = "0 (negative) - 10 (positive)", 
       x = "") +
  geom_hline(yintercept = 5, linetype = "dotted", color = "darkgrey") +
  theme_minimal() +
  scale_color_manual(values = fig_cols) +
  coord_flip() +
  theme(plot.title = element_text(hjust = 0.5),
        legend.position="none",
        legend.title = element_blank()) 
```
